---
title: "Rworksheet.Sabando#3b.Rmd"
author: "Samantha L. Sabando"
date: "2025-10-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# Create the dataset
# Creating the dataset based on the given table
#A
data <- data.frame(
  Respondents = 1:20,
  Sex = c(2,2,1,2,2,2,2,2,2,1,1,2,2,2,2,1,2,2,1,2),
  Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,1,1,3,1,2,1),
  Persons_at_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_at_School = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Types_of_Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,2,3,3,3,3,2)
)

# Display the dataset
data
##   Respondents Sex Fathers_Occupation Persons_at_Home Siblings_at_School Types_of_Houses
#1            1   2                  1               5                  6               1
#2            2   2                  3               7                  4               2
#3            3   1                  3               3                  4               3
#4            4   2                  3               8                  1               1
#5            5   2                  1               5                  2               1
#6            6   2                  2               9                  1               3
#7            7   2                  3               6                  5               3
#8            8   2                  1               7                  3               1
#9            9   2                  1               8                  1               2
#10          10   1                  1               4                  2               3
#11          11   1                  3               7                  3               2
#12          12   2                  2               5                  2               3
#13          13   2                  1               4                  5               2
#14          14   2                  3               7                  5               2
#15          15   2                  1               8                  2               2
#16          16   1                  1               8                  1               3
#17          17   2                  3               3                  2               3
#18          18   2                  1              11                  5               3
#19          19   1                  2               7                  3               3
#20          20   2                  1               6                  2               2
# Get the structure of the data
#B
str(data)
#'data.frame':	20 obs. of  6 variables:
# $ Respondents       : int  1 2 3 4 5 6 7 8 9 10 ...
# $ Sex               : num  2 2 1 2 2 2 2 2 2 1 ...
# $ Fathers_Occupation: num  1 3 3 3 1 2 3 1 1 1 ...
# $ Persons_at_Home   : num  5 7 3 8 5 9 6 7 8 4 ...
# $ Siblings_at_School: num  6 4 4 1 2 1 5 3 1 2 ...
# $ Types_of_Houses   : num  1 2 3 1 1 3 3 1 2 3 ...

# Get the summary of the data
#B
summary(data)
##   Respondents      Sex        Fathers_Occupation Persons_at_Home Siblings_at_School Types_of_Houses
# Min.   : 1.0   Min.   :1.00   Min.   :1.00     Min.   : 3.00   Min.   :1.00     Min.   :1.000      
# 1st Qu.: 5.8   1st Qu.:2.00   1st Qu.:1.00     1st Qu.: 5.00   1st Qu.:2.00     1st Qu.:2.000      
# Median :10.5   Median :2.00   Median :1.50     Median : 7.00   Median :3.00     Median :2.000      
# Mean   :10.5   Mean   :1.75   Mean   :1.75     Mean   : 6.65   Mean   :2.75     Mean   :2.250      
# 3rd Qu.:15.2   3rd Qu.:2.00   3rd Qu.:3.00     3rd Qu.:8.00    3rd Qu.:4.25     3rd Qu.:3.000      
# Max.   :20.0   Max.   :2.00   Max.   :3.00     Max.   :11.00   Max.   :6.00     Max.   :3.000

#C
mean_siblings <- mean(data$Siblings_at_School)
is_mean_5 <- mean_siblings == 5
print(is_mean_5)
print(mean_siblings)
#[1] FALSE
#[1] 2.75

#D
subset_data <- data[1:2, ]
print(subset_data)
##  Respondents Sex Fathers_Occupation Persons_at_Home Siblings_at_School Types_of_Houses
#1           1   2                  1               5                  6               1
#2           2   2                  3               7                  4               2

#E
subset_data_2 <- data[c(3, 5), c(2, 4)]
print(subset_data_2)
#  Sex Persons_at_Home
#3   1               3
#5   2               5

#F
types_houses <- data$Types_of_Houses
print(types_houses)
# [1] 1 2 3 1 1 3 3 1 2 3 2 3 2 2 2 3 3 3 3 2

#G
male_farmers <- subset(data, Sex == 1 & Fathers_Occupation == 1)
print(male_farmers)
#   Respondents Sex Fathers_Occupation Persons_at_Home Siblings_at_School Types_of_Houses
#10          10   1                  1               4                  2               3
#16          16   1                  1               8                  1               3

#H
female_many_siblings <- subset(data, Sex == 2 & Siblings_at_School >= 5)
print(female_many_siblings)
#  Respondents Sex Fathers_Occupation Persons_at_Home Siblings_at_School Types_of_Houses
#1           1   2                  1               5                  6               1
#7           7   2                  3               6                  5               3
#13         13   2                  1               4                  5               2
#18         18   2                  1              11                  5               3

```
```{r 2}
#2
df <- data.frame(Ints = integer(),
                 Doubles = double(),
                 Characters = character(),
                 Logicals = logical(),
                 Factors = factor(),
                 stringsAsFactors = FALSE)
print("Structure of the empty dataframe:")
print(str(df))
# [1] "Structure of the empty dataframe:"
# 'data.frame':	0 obs. of  5 variables:
#  $ Ints      : int(0) 
#  $ Doubles   : num(0)
#  $ Characters: chr(0) 
#  $ Logicals  : logi(0)
#  $ Factors   : Factor w/ 0 levels

#3
data <- read.csv("HouseholdData.csv")
print(data)
#   Respondents    Sex Fathers.Occupation Persons.at.Home Siblings.at.School Types.of.Houses
# 1            1   Male                  1               5                  2              Wood
# 2            2 Female                  2               7                  3          Congrete
# 3            3 Female                  3               3                  0          Congrete
# 4            4   Male                  3               8                  5              Wood
# 5            5   Male                  1               6                  2     Semi-congrete
# 6            6 Female                  2               4                  3     Semi-congrete
# 7            7 Female                  2               4                  1              Wood
# 8            8   Male                  3               2                  2     Semi-congrete
# 9            9 Female                  1              11                  6     Semi-congrete
#10          10   Male                  3               6                  2          Congret

#B
data$Sex <- factor(data$Sex, levels = c("Male", "Female"), labels = c(1, 2))
print(data$Sex)
# [1] 1 2 2 1 1 2 2 1 2 1
# Levels: 1 2

#C
data$Types.of.Houses <- factor(data$Types.of.Houses, levels = c("Wood", "Congrete", "Semi-congrete"), labels = c(1, 2, 3))
print(data$Types.of.Houses)
# [1] 1 2 2 1 3 3 1 3 2 2
# Levels: 1 2 3

#D
data$Fathers.Occupation <- factor(data$Fathers.Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
print(data$Fathers.Occupation)
#  [1] Farmer Driver Driver Others Farmer Driver Driver Others Farmer Farmer
# Levels: Farmer Driver Others

#E
female_drivers <- subset(data, Sex == "2" & Fathers.Occupation == "Driver")
print(female_drivers)


#   Respondents Sex Fathers.Occupation Persons.at.Home Siblings.at.School Types.of.Houses
#2            2   2             Driver               7                  3                 2
#6            6   2             Driver               4                  3                 3
#7            7   2             Driver               4                  1                 1

#F
respondents_5_siblings <- subset(data, Siblings.at.School >= 5)
print(respondents_5_siblings)
#   Respondents Sex Fathers.Occupation Persons.at.Home Siblings.at.School Types.of.Houses
#4           4   1             Others               8                  5                 1
#9           9   2             Farmer              11                  6                 3

```{r 4}
# Figure 3:  Interpretation
# The bar chart illustrates the distribution of tweet sentiments per day 
# from July 14 to July 21, 2020. Negative sentiments consistently appear 
# as the most dominant category, peaking notably on July 15 and July 21. 
# Neutral tweets show relatively stable counts throughout the observed period, 
# while positive tweets remain lower but display minor increases on certain days 
# such as July 17 and July 20. Overall, the figure indicates that Twitter users 
# expressed more negative sentiments during this timeframe compared to neutral 
# and positive reactions.
```



