---
title: "Rworksheet.Sabando.#3b.Rmd"
author: "Samantha L. Sabando"
date: "2025-11-24"
output: pdf_document
---

```{r}
# Create the dataset
# Creating the dataset based on the given table
#A
data <- data.frame(
  Respondents = 1:20,
  Sex = c(2,2,1,2,2,2,2,2,2,1,1,2,2,2,2,1,2,2,1,2),
  Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,1,1,3,1,2,1),
  Persons_at_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_at_School = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Types_of_Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,2,3,3,3,3,2)
)

# Display the dataset
data

#B
str(data)

# Get the summary of the data
#B
summary(data)

#C mean number
mean_siblings <- mean(data$Siblings_at_School)
is_mean_5 <- mean_siblings == 5
print(is_mean_5)
print(mean_siblings)

#D The 1st two rows and then all the columns using the subsetting functions
subset_data <- data[1:2, ]
print(subset_data)

#E 3rd and 5th row with 2nd and 4th column
subset_data_2 <- data[c(3, 5), c(2, 4)]
print(subset_data_2)

#F the variable types of houses then store the vector that results as types_houses
types_houses <- data$Types_of_Houses
print(types_houses)


#G only all Males respondent that their father occupation was farmer
male_farmers <- subset(data, Sex == 1 & Fathers_Occupation == 1)
print(male_farmers)


#H only all females respondent that have greater than or equal to 5 number of siblings attending school
female_many_siblings <- subset(data, Sex == 2 & Siblings_at_School >= 5)
print(female_many_siblings)

```
```{r 2}
#A Create an empty data frame
df <- data.frame(Ints = integer(),
                 Doubles = double(),
                 Characters = character(),
                 Logicals = logical(),
                 Factors = factor(),
                 stringsAsFactors = FALSE)
print("Structure of the empty dataframe:")
print(str(df))


#B Read the CSV file
data <- read.csv("HouseholdData.csv")
print(data)


#C Convert Sex into factor
data$Sex <- factor(data$Sex,
                   levels = c(1, 2),
                   labels = c("Male", "Female"))
print(data$Sex)


#D Convert Type of Houses into factor
data$Types.of.Houses <- factor(data$Types.of.Houses,
                               levels = c(1, 2, 3),
                               labels = c("Wood", "Concrete", "Semi-concrete"))
print(data$Types.of.Houses)


#E Convert Fathers Occupation into factor
data$Fathers.Occupation <- factor(data$Fathers.Occupation,
                                  levels = c(1, 2, 3),
                                  labels = c("Farmer", "Driver", "Others"))
print(data$Fathers.Occupation)


#F Select all female respondents whose father is a driver
female_drivers <- subset(data,
                         Sex == "Female" &
                         Fathers.Occupation == "Driver")
print(female_drivers)


#G Select respondents with >= 5 siblings at school
respondents_5_siblings <- subset(data,
                                 Siblings.at.School >= 5)
print(respondents_5_siblings)


```{r 4}
# Figure 3:  Interpretation
# The bar chart illustrates the distribution of tweet sentiments per day 
# from July 14 to July 21, 2020. Negative sentiments consistently appear 
# as the most dominant category, peaking notably on July 15 and July 21. 
# Neutral tweets show relatively stable counts throughout the observed period, 
# while positive tweets remain lower but display minor increases on certain days 
# such as July 17 and July 20. Overall, the figure indicates that Twitter users 
# expressed more negative sentiments during this timeframe compared to neutral 
# and positive reactions.
```



